### 2018-09-03 paper/conclusion.tex
some more suggestions

% ==============================================================================
\subsubsection*{Discussion of Further Reductions of the Test Effort}
It is known from complete testing strategies for finite state machines that
the upper bound $pq$ for the lengths of the traces used in our tests to
investigate the SUT behaviour can be reduced. It is also known from FSM
testing that it is not necessary to test {\it all} traces up to this maximal
length. Notable complete strategies supporting this fact have been presented,
for example,
in~\cite{hierons_testing_2004,DBLP:conf/forte/DorofeevaEY05,petrenko_testing_2011,simao_reducing_2012}.
From~\cite{Huang2017} it is known that complete FSM testing theories can be
translated to other formalisms, such as Extended Finite State Machines,
Kripke Structures, or CSP, resulting in likewise complete test strategies for
the latter. We intend to study translations of several promising FSM
strategies to CSP in the future. These will effectively reduce the upper
bound $\ell\le |\Sigma|^k$ introduced in Section~\ref{sec:complexity}. The
bound $h$ for the number of sets to be used in probing the SUT for illegal
deadlocks, however, cannot be further reduced, as has been established in
Lemma~\ref{lemma:hseta}. \fixme{alcc: my guess is that these complete tests
are not for refinement. I think we can perhaps say something about this?}

@@

In contrast to that, our test cases specified in
Section~\ref{sec:finitecompletefails} and \ref{sec:finitecomplete} are
adaptive. This has the advantage that test executions $(Q\parallel[\Sigma]
U_F(p))$ for failures refinement never blocks before the final step specified
by branch (\ref{eq:ufd}), and so we do not need inconclusive test results. It
should be noted, however, that it is necessary for our test verdicts to
recognise also deadlocks in the final test step and interpret them as FAIL,
as described in Section~\ref{sec:finitecompletefails}. In practice, this is
realised by adding a timeout event to the testing environment which indicates
deadlock situations. For real-time systems, this is an accepted technique,
because the SUT has to respond within a pre-defined latency interval,
otherwise its behaviour is considered to be blocked and regarded as a
failure. \fixme{alcc: if deadlock is not acceptable?}

@@

% ==============================================================================
\subsubsection*{Discussion of Fault Domains}
As already mentioned, the work in~\cite{DBLP:conf/pts/CavalcantiS17} defines
a fault domain as the set of processes that refine a given CSP process.  In
that context, only testing for traces refinement is considered, and the
complete test suites may not be finite. So, the work presented here go well
beyond what is achieved there. On the other hand,
\cite{DBLP:conf/pts/CavalcantiS17} presents an algorithm for test generation
that can be easily adapted to consider additional selection and termination
criteria, like, for example, the length of the traces used to construct
tests. It would be possible, for instance, to use the bound indicated here.
Morevoer, specifying a fault domain as a CSP process allows us to model
domain-specific knowledge using CSP. For example, if an initialisation
component defined by a process $I$ can be regarded as correct without further
testing, we can use $I; RUN$ as a fault domain, to indicate that any SUT of
interest implements $I$ correctly, but afterwards has a potentially arbitrary
behaviour specified by $RUN$.

>>>>

% ==============================================================================
\subsubsection*{Discussion of Further Reductions of the Test Effort}
It is known from complete testing strategies for finite state machines that
the upper bound $pq$ for the lengths of the traces used in our tests to
investigate the SUT behaviour can be reduced. It is also known from FSM
testing that it is not necessary to test {\it all} traces up to this maximal
length. Notable complete strategies supporting this fact have been presented,
for example,
in~\cite{hierons_testing_2004,DBLP:conf/forte/DorofeevaEY05,petrenko_testing_2011,simao_reducing_2012}.
From~\cite{Huang2017} it is known that complete FSM testing theories can be
translated to other formalisms, such as Extended Finite State Machines,
Kripke Structures, or CSP, resulting in likewise complete test strategies for
the latter. We intend to study translations of several promising FSM
strategies to CSP in the future. These will effectively reduce the upper
bound $\ell\le |\Sigma|^k$ introduced in Section~\ref{sec:complexity}. The
bound $h$ for the number of sets to be used in probing the SUT for illegal
deadlocks, however, cannot be further reduced, as has been established in
Lemma~\ref{lemma:hseta}.

@@

In contrast to that, our test cases specified in
Section~\ref{sec:finitecompletefails} and \ref{sec:finitecomplete} are
adaptive. This has the advantage that test executions $(Q\parallel[\Sigma]
U_F(p))$ for failures refinement never blocks before the final step specified
by branch (\ref{eq:ufd}), and so we do not need inconclusive test results. It
should be noted, however, that it is necessary for our test verdicts to
recognise also deadlocks in the final test step and interpret them as FAIL,
as described in Section~\ref{sec:finitecompletefails}. In practice, this is
realised by adding a timeout event to the testing environment which indicates
deadlock situations. For real-time systems, this is an accepted technique,
because the SUT has to respond within a pre-defined latency interval,
otherwise its behaviour is considered to be blocked and regarded as a
failure. \fixme{alcc: if deadlock is not acceptable? I think you need
instrumentation here as well. }

@@

% ==============================================================================
\subsubsection*{Discussion of Fault Domains}
As already mentioned, the work in~\cite{DBLP:conf/pts/CavalcantiS17} defines
a fault domain as the set of processes that refine a given CSP process.  In
that context, only testing for traces refinement is considered, and the
complete test suites may not be finite. So, the work presented here go well
beyond what is achieved there. On the other hand,
\cite{DBLP:conf/pts/CavalcantiS17} presents an algorithm for test generation
that can be easily adapted to consider additional selection and termination
criteria, like, for example, the length of the traces used to construct
tests. It would be possible, for instance, to use the bound indicated here.
Morevoer, specifying a fault domain as a CSP process allows us to model
domain-specific knowledge using CSP. For example, if an initialisation
component defined by a process $I$ can be regarded as correct without further
testing, we can use $I; RUN$ as a fault domain, to indicate that any SUT of
interest implements $I$ correctly, but afterwards has a potentially arbitrary
behaviour specified by $RUN$. The work in~\cite{DBLP:conf/pts/CavalcantiS17}
is not restricted to finite or non-terminating processes.
